Manuscript Figures for Genome Biology

### 2018-10-25 manuscript_figures/manuscript_figures_main.Rmd
Make alpha threshold consistent for Fcase study results figure

## read in case study results (proportion of rejects vs. case study max)
objdat <- tidy_df(objects=objects, colLabels=object_labs, 
                  fill="propMaxRejections", annotate=NULL,
                  alpha =0.10)
objdat <- as_tibble(objdat)
objdat <- tidyr::complete(objdat, method, casestudy)

>>>>

## read in case study results (proportion of rejects vs. case study max)
objdat <- tidy_df(objects=objects, colLabels=object_labs, 
                  fill="propMaxRejections", annotate=NULL,
                  alpha = alpha.thresh)
objdat <- as_tibble(objdat)
objdat <- tidyr::complete(objdat, method, casestudy)
